\vspace{-\baselineskip} Fast and scalable Gaussian process modeling with applications to astronomical time series \vspace{-2\baselineskip}

### 2017-06-12 paper/ms.tex
author order

\author{%
    Daniel~Foreman-Mackey\altaffilmark{\sagan,\uw},
    Eric~Agol\altaffilmark{\uw,\guggenheim},
    Ruth~Angus\altaffilmark{\simons,\columbia}, and
    Sivaram~Ambikasaran\altaffilmark{\iis}
}

>>>>

\author{%
    Daniel~Foreman-Mackey\altaffilmark{\sagan,\uw},
    Eric~Agol\altaffilmark{\uw,\guggenheim},
    Sivaram~Ambikasaran\altaffilmark{\iis}, and
    Ruth~Angus\altaffilmark{\simons,\columbia}
}
